Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
Additional packages to help reduce white space
Removes autocites

Lua performs well as an embeddable scripting language. Although it is an
interpreted language, the bindings are designed to make the exchange of
variables and functions amongst languages straightforward. The LuaJIT
virtual machine boasts near-native performance, making it a logical
choice for scriptability frameworks in systems research
\autocite{neto:dls14-luaos}. In storage systems, it has been effectively
used both on \autocites[
]{grawinkel:pdsw2012-lua}{watkins2013:bdmc13-in-vivo} and off
\autocite{sevilla:sc15-mantle} the critical path, where performance is
important.

@@

The other two advantages, that Lua leaves a small memory footprint and
that it is secure, are discussed at length in \autocites[
]{ierusalimschy_programming_2006}{neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the
system against some malicious cases, but does not protect the system
from poor policies. Since Malacology does not use these features (yet),
we will avoid discussion here.

>>>>

Lua performs well as an embeddable scripting language. Although it is an
interpreted language, the bindings are designed to make the exchange of
variables and functions amongst languages straightforward. The LuaJIT
virtual machine boasts near-native performance, making it a logical
choice for scriptability frameworks in systems research
\cite{neto:dls14-luaos}. In storage systems, it has been effectively
used both on \cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo} and off
\cite{sevilla:sc15-mantle} the critical path, where performance is
important.

@@

The other two advantages, that Lua leaves a small memory footprint and
that it is secure, are discussed at length in 
\cite{ierusalimschy_programming_2006,neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the
system against some malicious cases, but does not protect the system
from poor policies. Since Malacology does not use these features (yet),
we will avoid discussion here.
